Analytic Occultation Light Curves in Reflected Light

### 2020-04-06 tex/ms.tex
finished casses

\section{The Solution: Occultation}
\label{sec:solution-occ}
%
The integration in the unocculted case presented above is relatively
straightforward, since
the boundaries of integration are always the half-ellipse defining the
terminator and the half-circle defining the upper limb of the body
(Equation~\ref{eq:rT}). When an occultor is present, however, the
integration boundaries are far less trivial, since they may or may not
include sections of the terminator, sections of the limb of the body,
and sections of the limb of the occultor. There are in total ten families of
configurations, each defined by a distinct combination of integration
boundaries; these are shown in Figures~\ref{fig:cases} and
\ref{fig:pathological}.
Together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position.

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight principal families of cases of occultations in
            reflected light.
            In these figures, the body with the solid outline
            is the one whose flux we are interested in, and the body with the
            dashed outline is the occultor.
            The night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted).
            The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the orange boundary (the curves
            $P$, $T$, and $Q$ of
            \S\ref{sec:cases-5-8}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

@@

Cases with zero roots (case 1 -- case 4) are treated in \S\ref{sec:cases-1-4},
while cases with one or two roots (case 5 -- case 8) are treated in
\S\ref{sec:cases-5-8}. Cases with three or four roots
(case 9 -- case 10) are rarely encountered
in practice, but are possible for some pathological configurations; these are
treated in \S\ref{sec:cases-9-10}.

@@

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve. In particular, we can use the original emitted
light solution from \citet{Luger2019}, provided we weight the map by our
polynomial illumination function:
%
\begin{proof}{}
    \label{eq:fI}
    f_I &=
    \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{proof}
%
where $\sTe(b_o, r_o)$ is the emitted light solution vector
\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
measure from a body whose surface map is weighted by the illumination function
$\BF{I}(b, \theta', r_s)$ during an occultation. Note that this is not
necessarily the \emph{observed} flux, since this may include the unphysical
negative contribution from the nightside. We must compute the actual
observed flux on a case-by-case basis.

Case 1 corresponds to any complete occultation of the body
($b_o \le r_o - 1$), so the solution for the flux is trivial:
%
\begin{align}
    \label{eq:f1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:f2}
    f_2 = f_0
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside, and
we can simply use the weighted solution in emitted light
(Equation~\ref{eq:fI}):
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = f_\mathrm{I}
\end{proof}
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb). We first compute the illumination-weighted flux
$f_I$ as above, then negate the unphysical nightside contribution
using Equation~(\ref{eq:f0hat}):
%
\begin{proof}{}
    \label{eq:f4}
    f_4 = f_I - \hat{f}_0
    \quad.
\end{proof}

@@

\subsection{Cases 5--8}
\label{sec:cases-5-8}
%

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/geometry.pdf}
        \oscaption{geometry}{%
            Geometry of an occultation in reflected light, corresponding
            to case 5 in Figure~\ref{fig:cases}. The surface integral over
            the occulted portion of the dayside (light gray region)
            is computed from the line integrals of the antiderivatives of the
            surface intensity map along the boundary curves
            $P$, $T$, and $Q$. See text for details.
            \label{fig:geometry}
        }
    \end{centering}
\end{figure}

Cases 5--8 (see Figure~\ref{fig:cases}) correspond to configurations in which
the limb of the occultor intersects with the terminator at either one point
(case 5) or two points (cases 6, 7, and 8). Because of these intersections, we
cannot simply re-weight the emitted light solution, as the integration
boundaries are now different. In general, we may compute the flux by
integrating the components of the Green's basis $\bg$
over the region $S$ bounded by three curves, which we denote
$P$, $T$, and $Q$. These are shown in orange
in Figure~\ref{fig:cases} and presented in more detail in
Figure~\ref{fig:geometry}.
Curve $P$ is a segment of the limb of
the occultor, parametrized by the angle $\phi \in [\phi_1, \phi_2]$;
curve $T$ is a segment of the terminator,
parametrized by the angle $\xi \in [\xi_1, \xi_2]$;
and curve $Q$ is a segment of the limb of the occulted body,
parametrized by the angle $\lambda \in [\lambda_1, \lambda_2]$.
The endpoints $\phi_1, \phi_2, \xi_1, \xi_2, \lambda_1,$ and
$\lambda_2$ are functions of the solutions to the quartic from
\S\ref{sec:which-case} and will be presented below.

As in \citet{Luger2019}, the approach to computing the surface integrals
of each of the terms in $\bg$ over $S$
is to use Green's theorem to transform them into line integrals along the
curves $P$, $T$, and $Q$. Let $\mathfrak{p}^\top$,
$\mathfrak{t}^\top$, and $\mathfrak{q}^\top$ denote the vectors
corresponding to the line integrals
along the curves $P$, $T$, and $Q$, respectively, for each of the terms in
$\bg$. The integration is performed in the frame $\mathcal{F}'$,
in a counter-clockwise direction relative to the center
of the integration region $S$.
Then the integral of $\bg$ over $S$ is%
\footnote{%
    The components of the vectors $\mathfrak{p}^\top$ and
    $\mathfrak{q}^\top$ are analogous to the ``primitive integrals''
    $\mathcal{P}$ and $\mathcal{Q}$
    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
    integration limits of both and the sense of integration of $\mathcal{P}$
    are different.
}
%
\begin{align}
    \label{eq:sT}
    \sT & =
    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
    \quad,
\end{align}
%
where the dependence on $b, \theta', b_o,$ and $r_o$ is implicit.
%
We defer the solution to Equation~(\ref{eq:sT}) to \S\ref{sec:sT} below,
as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
region $S$ is computed from Equation~(\ref{eq:sTA2IA1RRy}):
%
\begin{align}
    \label{eq:fS}
    f_S & =
    \mathfrak{s}^\top(b, \theta', b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{align}
%
Note again that this is not necessarily the \emph{observed} flux, which we must
compute on a case-by-case basis below.

Case 5 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 6--8 involve two points of intersection between the occultor limb and
the terminator. The region we integrate over is bounded only by the terminator
and the limb of the occultor, so when computing $f_S$ below we set
$\mathfrak{q}^\top = \boldsymbol{0}$.
%
Case 6 corresponds to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. We begin by computing the
flux over the unocculted region, $f_3$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Cases 7 and 8 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 7
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{proof}{}
    \label{eq:7}
    f_7 = f_I - f_S
    \quad.
\end{proof}
%
Conversely, case 8 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_S
    \quad.
\end{proof}
%

\subsection{Cases 9--10}
\label{sec:cases-9-10}

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pathological.pdf}
        \oscaption{pathological}{%
            Two additional families of occultations in reflected light,
            involving rare triple (case 9, left) and quadruple
            (case 10, right) intersections between the limb of the
            occultor and the terminator of the occulted body. Both cases
            involve integration over two disjoint regions (bounded by
            the orange curves in the figure). The insets next to each case
            show a zoomed-in version of two such regions. See text for
            more details.
            \label{fig:pathological}
        }
    \end{centering}
\end{figure}

Finally, cases 9 and 10 correspond to (rare) configurations involving three
or four roots to Equation~\ref{eq:quartic}, respectively, and are
illustrated in Figure~\ref{fig:pathological}.

>>>>

\section{The Solution: Occultation}
\label{sec:solution-occ}
%
The integration in the unocculted case presented above is relatively
straightforward, since
the boundaries of integration are always the half-ellipse defining the
terminator and the half-circle defining the upper limb of the body
(Equation~\ref{eq:rT}). When an occultor is present, however, the
integration boundaries are far less trivial, since they may or may not
include sections of the terminator, sections of the limb of the body,
and sections of the limb of the occultor. There are in total 14 families of
configurations, each defined by a distinct combination of integration
boundaries; these are shown in Figures~\ref{fig:cases} and
\ref{fig:pathological}.
Together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position.

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The 10 principal families of cases of occultations in
            reflected light.
            In these figures, the body with the solid outline
            is the one whose flux we are interested in, and the body with the
            dashed outline is the occultor.
            The nightside of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (bluish-grey if occulted).
            Case 0 is the unocculted case (\S\ref{sec:solution-no-occ}),
            while cases 1--5 involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the orange boundary (the curves
            $P$, $T$, and $Q$ of
            \S\ref{sec:cases-hard}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

@@

Cases with zero roots (case 1 -- case 4) are treated in \S\ref{sec:cases-easy},
while cases with one or two roots (case 5 -- case 8) are treated in
\S\ref{sec:cases-hard}. Cases with three or four roots
(case 9 -- case 10) are rarely encountered
in practice, but are possible for some pathological configurations; these are
treated in \S\ref{sec:cases-pathological}.

@@

\subsection{Cases 1--5}
\label{sec:cases-easy}
%
Cases 1--5 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve. In particular, we can use the original emitted
light solution from \citet{Luger2019}, provided we weight the map by our
polynomial illumination function:
%
\begin{proof}{}
    \label{eq:fI}
    f_I &=
    \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{proof}
%
where $\sTe(b_o, r_o)$ is the emitted light solution vector
\citep[Equation~26 in][]{Luger2019}. The flux $f_I$ is the flux one would
measure from a body whose surface map is weighted by the illumination function
$\BF{I}(b, \theta', r_s)$ during an occultation. Note that this is not
necessarily the \emph{observed} flux, since this may include the unphysical
negative contribution from the nightside. We must compute the actual
observed flux on a case-by-case basis.

Case 1 corresponds to any complete occultation of the body
($b_o \le r_o - 1$), so the solution for the flux is trivial:
%
\begin{align}
    \label{eq:f1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 corresponds to occultations in which the occultor blocks \emph{all} of
the dayside of the body and \emph{some} of the nightside. In this
configuration, the unocculted part of the disk consists only of nightside, so
the solution is again trivial:
%
\begin{align}{}
    \label{eq:f2}
    f_2 = 0
    \quad.
\end{align}
%
Conversely, case 3 corresponds to occultations in which the occultor blocks
\emph{all} of the nightside of the body and \emph{some} of the dayside.
Since the visible portion of the disk consistss only of dayside, we can
simply use the weighted solution in emitted light
(Equation~\ref{eq:fI}):
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = f_\mathrm{I}
\end{proof}
%
Case 4 involves any occultation in which the occultor blocks \emph{only} the
nightside of the body (regardless of whether or not it intersects with the
limb of the body). Since the nightside intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:f4}
    f_2 = f_0
    \quad.
\end{align}
%
Finally, case 5 involves any occultation in which the occultor blocks
\emph{only} the dayside of the body (regardless of whether or not it
intersects with the limb). We first compute the illumination-weighted flux
$f_I$ as above, then negate the unphysical nightside contribution
using Equation~(\ref{eq:f0hat}):
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_I - \hat{f}_0
    \quad.
\end{proof}

@@

\subsection{Cases 6--10}
\label{sec:cases-hard}
%

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/geometry.pdf}
        \oscaption{geometry}{%
            Geometry of an occultation in reflected light, corresponding
            to case 6 in Figure~\ref{fig:cases}. The surface integral over
            the occulted portion of the dayside (bluish-grey region)
            is computed from the line integrals of the antiderivatives of the
            surface intensity map along the boundary curves
            $P$, $T$, and $Q$. See text for details.
            \label{fig:geometry}
        }
    \end{centering}
\end{figure}

Cases 6--10 (see Figure~\ref{fig:cases}) correspond to configurations in which
the limb of the occultor intersects with the terminator at either one point
(case 6) or two points (cases 7--10). Because of these intersections, we
cannot simply re-weight the emitted light solution, as the integration
boundaries are now different. In general, we may compute the flux by
integrating the components of the Green's basis $\bg$
over the region $S$ bounded by three curves, which we denote
$P$, $T$, and $Q$. These are shown in orange
in Figure~\ref{fig:cases} and presented in more detail in
Figure~\ref{fig:geometry}.
Curve $P$ is a segment of the limb of
the occultor, parametrized by the angle $\phi \in [\phi_1, \phi_2]$;
curve $T$ is a segment of the terminator,
parametrized by the angle $\xi \in [\xi_1, \xi_2]$;
and curve $Q$ is a segment of the limb of the occulted body,
parametrized by the angle $\lambda \in [\lambda_1, \lambda_2]$.
The endpoints $\phi_1, \phi_2, \xi_1, \xi_2, \lambda_1,$ and
$\lambda_2$ are functions of the solutions to the quartic from
\S\ref{sec:which-case} and will be presented below.

As in \citet{Luger2019}, the approach to computing the surface integrals
of each of the terms in $\bg$ over $S$
is to use Green's theorem to transform them into line integrals along the
curves $P$, $T$, and $Q$. Let $\mathfrak{p}^\top$,
$\mathfrak{t}^\top$, and $\mathfrak{q}^\top$ denote the vectors
corresponding to the line integrals
along the curves $P$, $T$, and $Q$, respectively, of the anti-exterior
derivatives of each of the terms in
$\bg$ (see Appendix~\ref{sec:sT}).
The integration is performed in the frame $\mathcal{F}'$,
in a counter-clockwise direction relative to the center
of the integration region $S$.
Then the integral of $\bg$ over $S$ is%
\footnote{%
    The components of the vectors $\mathfrak{p}^\top$ and
    $\mathfrak{q}^\top$ are analogous to the ``primitive integrals''
    $\mathcal{P}$ and $\mathcal{Q}$
    defined in Equations~(30)--(32) in \citet{Luger2019}, although the
    integration limits of both (and the sense of integration of $\mathcal{P}$)
    are different.
}
%
\begin{align}
    \label{eq:sT}
    \sT & =
    \mathfrak{p}^\top + \mathfrak{t}^\top + \mathfrak{q}^\top
    \quad,
\end{align}
%
where the dependence on $b, \theta', b_o,$ and $r_o$ is implicit.
%
We defer the solution to Equation~(\ref{eq:sT}) to \S\ref{sec:sT} below,
as it is quite lengthy. Given $\sT$, the flux $f_S$ over the integration
region $S$ is computed from Equation~(\ref{eq:sTA2IA1RRy}):
%
\begin{align}
    \label{eq:fS}
    f_S & =
    \mathfrak{s}^\top(b, \theta', b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{align}
%
Note again that this is not necessarily the \emph{observed} flux, which we must
compute on a case-by-case basis below.

Case 6 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 7--10 involve two points of intersection between the occultor limb and
the terminator. The region we integrate over is bounded only by the terminator
and the limb of the occultor, so when computing $f_S$ below we set
$\mathfrak{q}^\top = \boldsymbol{0}$.
%
Cases 7 and 8 correspond to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. In case 7 a lens-shaped region is formed by the
intersection of the occultor limb and the terminator on the
\emph{nightside}, while in case 8 this region is formed on the \emph{dayside}.
%
In case 7, we begin by computing the
flux over the unocculted region, $f_I$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f7}
    f_7 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Case 8, on the other hand, is topologically equivalent to case 6, since
the integration region consists of occulted dayside:
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 9 and 10 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 9
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{proof}{}
    \label{eq:f9}
    f_9 = f_I - f_S
    \quad.
\end{proof}
%
Conversely, case 10 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{proof}{}
    \label{eq:f10}
    f_{10} = f_S
    \quad.
\end{proof}
%

\subsection{Cases 11--14}
\label{sec:cases-pathological}

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pathological.pdf}
        \oscaption{pathological}{%
            Four additional families of occultations in reflected light,
            involving rare triple (cases 11 and 12, top) and quadruple
            (cases 13 and 14, bottom) intersections between the limb of the
            occultor and the terminator of the occulted body. All four cases
            involve integration over two disjoint regions (bounded by
            the orange curves in the figure). The insets next to each case
            show a zoomed-in version of four such regions. See text for
            more details.
            \label{fig:pathological}
        }
    \end{centering}
\end{figure}

Cases 11--14 correspond to (rare) configurations involving three
or four roots to Equation~\ref{eq:quartic} and are
illustrated in Figure~\ref{fig:pathological}. All four involve integration over
two disjoint regions (see the figure).
%
Cases 11 and 12 involve three points of intersection between the terminator
and the occultor limb. In case 11, the regions of integration $S_1$ and
$S_2$ are the
occulted portion of the dayside, so the solution is similar to
that of cases 6 and 8:
%
\begin{proof}{}
    \label{eq:f11}
    f_{11} = f_0 - (f_{S_1} + f_{S_2})
    \quad,
\end{proof}
%
where $f_{S_1}$ and $f_{S_2}$ are computed from Equation~(\ref{eq:fS}) for
each of the integration regions. Conversely, in case 12 the two regions
are the occulted portion of the nightside, so the solution is similar to that
of case 7:
%
\begin{proof}{}
    \label{eq:f12}
    f_{12} = f_I - \big(\hat{f}_0 - (f_{S_1} + f_{S_2})\big)
    \quad,
\end{proof}
%
Finally, cases 13 and 14 involve four points of intersection between the
terminator and the occultor limb. The regions of integration in case 13 are
the visible portion of the nightside, so this case is equivalent to case 9:
%
\begin{proof}{}
    \label{eq:f13}
    f_{13} = f_I - (f_{S_1} + f_{S_2})
    \quad.
\end{proof}
%
Conversely, the regions of integration in case 14 are the
visible portion of the dayside, so this case is equivalent to case 10:
%
\begin{proof}{}
    \label{eq:f14}
    f_{14} = (f_{S_1} + f_{S_2})
    \quad.
\end{proof}
%
